Variations on a Bayesian Theme: Comparing Bayesian Models of Referential Reasoning

### 2014-03-18 02_RSA.tex
final

To test these intuitions, Frank \& Goodman recruited 745 US
participants via Amazon's Mechanical Turk to take part in a one-shot
referential game, either as the speaker or the listener \cite{Frank}.
The context of the game always consisted of three objects (e.g.,
Figure~\ref{context}).  Each object had three features: color (red,
blue, or green), shape (circle, square, or cloud), and texture (solid,
or polka-dot, or striped).  Every context had one feature fixed for
all objects and the other two features systematically varied.  The
objects were randomly permuted and the target object was randomly
assigned.  Depending on how many objects shared the same value of a
feature with the target, contexts were classified into 7 categories
(Fig.~\ref{fig:fg-all}):
1/1, 1/2 (the target's first feature is unique, and there is another
object sharing the same value of the second feature with the target),
1/3, 2/2 with the same object sharing both features with the target
(which means there is another object identical to the target), 2/2
with different objects sharing the features, 2/3 and 3/3.  
The speakers were asked to choose a
feature to refer to the target object.\footnote{More accurately,
  participants were ask to \emph{bet} on features and referents. We
  will discuss this design choice when contrasting it with our 
  replication in Section~\ref{sec:experiment}.}  In order
to measure the perceptual salience, some of the listeners were told
that the speaker was using a language that they did not understand and
then they were asked to guess the intended referent.  Other listeners
were told a feature of the target and asked to choose the intended
referent. 
Note that listeners were presented with pictures without dotted lines 
surrounding the target so they did not know the target.
For each category in each of the speaker, salience and listener conditions, 
there were roughly 50 responses\footnote{As we can see, despite the fairly 
large number of participants recruited, the data in each condition 
are not that many. Also there might be concern that some conditions might 
look less interesting than others. Again we will discuss these issues when 
we introduce our own replication in Section~\ref{sec:experiment}. Here
we note that variety is important in order to test the general validity of 
a pragmatic theory. 
Thus the design used in \cite{Frank} served its purposes well, but may be 
adapted when the goal is different.}.

The result of the experiment showed that speakers generally followed
Grice's Maxim of Quantity, i.e., they tried to be informative by
choosing the most unique feature of the target\footnote{Speakers' preference
was not taken into account in \cite{Frank}, so all features were randomly 
assigned and later lumped together in the analysis.}, and that listeners
were influenced by both the perceptual salience and the
informativeness of the utterance that the speaker produced. However,
the data, being quantitative in nature, cannot be fully explained by a
classical qualitative Gricean account of scalar implicatures, so that
a major challenge in terms of formal modeling becomes how to quantify
notions such as informativeness and perceptual salience, and how these
should be integrated to yield qualitative predictions.

>>>>

To test these intuitions, Frank \& Goodman recruited 745 US
participants via Amazon's Mechanical Turk to take part in a one-shot
referential game, either as the speaker or the listener \cite{Frank}.
The context of the game always consisted of three objects (e.g.,
Figure~\ref{context}).  Each object had three features: color (red,
blue, or green), shape (circle, square, or cloud), and texture (solid,
or polka-dot, or striped).  Every context had one feature fixed for
all objects and the other two features systematically varied.  The
objects were randomly permuted and the target object was randomly
assigned.  Depending on how many objects shared the same value of a
feature with the target, contexts were classified into 7 categories
(see Fig.~\ref{fig:fg-all}): 1/1, 1/2 (the target's first feature is
unique, and there is another object sharing the same value of the
second feature with the target), 1/3, 2/2 with the same object sharing
both features with the target (which means there is another object
identical to the target), 2/2 with different objects sharing the
features, 2/3 and 3/3.  The speakers were asked to choose a feature to
refer to the target object.\footnote{More accurately, participants
  were ask to \emph{bet} on features and referents. We will discuss
  this design choice when contrasting it with our replication in
  Section~\ref{sec:experiment}.}  In order to measure the perceptual
salience, some of the listeners were told that the speaker was using a
language that they did not understand and then they were asked to
guess the intended referent.  Other listeners were told a feature of
the target and asked to choose the intended referent.  Note that
listeners were presented with pictures without dotted lines
surrounding the target so they did not know the target.  For each
category in each of the speaker, salience and listener conditions,
there were roughly 50 responses.\footnote{As we can see, despite the
  fairly large number of participants recruited, the data in each
  condition are not that many. Also there might be a concern that some
  conditions might look less interesting than others. Again we will
  discuss these issues when we introduce our own replication in
  Section~\ref{sec:experiment}. Here we note that variety is important
  in order to test the general validity of a pragmatic theory.  Thus
  the design used in \cite{Frank} served its purposes well, but may be
  adapted when the goal is different.}

The result of the experiment showed that speakers generally followed
Grice's Maxim of Quantity, i.e., they tried to be informative by
choosing the most unique feature of the target,\footnote{Speakers'
  preference was not taken into account in \cite{Frank}, so all
  features were randomly assigned and later lumped together in the
  analysis.} and that listeners were influenced by both the perceptual
salience and the informativeness of the utterance that the speaker
produced. However, the data, being quantitative in nature, cannot be
fully explained by a classical qualitative Gricean account of scalar
implicatures, so that a major challenge in terms of formal modeling
becomes how to quantify notions such as informativeness and perceptual
salience, and how these should be integrated to yield qualitative
predictions.
